% Add option `kerning` to `microtype`. Since `acmart` already loads `microtype`
% by itself, we need to add this option here to hook into the package-loading
% process.
\PassOptionsToPackage{kerning}{microtype}
%
\documentclass[%
  anonymous=true,%
  authordraft=false,%
  format=sigconf,%
  review=false,%
  screen=true,%
  timestamp=false,%
  pbalance,%
]{acmart}

\copyrightyear{2024}


\usepackage{defs}
\usepackage{listings}
\lstset{escapeinside={<@}{@>}}
\usepackage{amsmath}
\usepackage{xcolor}
%\usepackage{lipsum,multicol}
\graphicspath{{./}{./img/}}

\input{macros}
\setlength {\marginparwidth }{2cm}
\begin{document}
%\begin{multicols}{2}

\title{A Python Decorator for Programmatic and Deterministic Unit Test Code Generation}

\author{James Hatfield}
\email{jahatfi@gmail.com}
\orcid{0009-0003-1677-0026}
\affiliation{
  \state{Maryland}
  \country{United States of America}
}


  
  \ccsdesc[300]{Software and its engineering~Software maintenance tools}
  \ccsdesc[500]{Software and its engineering~Software testing and debugging}
  \ccsdesc[500]{Software and its engineering~Empirical software validation}
  \ccsdesc[100]{Software and its engineering~Object oriented frameworks}
  \ccsdesc[100]{Software and its engineering~Object oriented development}

\begin{abstract}
  %
  % Context
  Automated software testing is an area of active research, 
  particularly automated generation of unit tests. 
  %
  % Problem
  Current and previous work such as generative AI, search-based heuristics, and 
  randomization often led to incomplete coverage and non-deterministic results.
  %
  In addition, some of the previous work lacks a natural way for a human expert 
  to provide input to the automated test generator outside the source code itself. 
  % Insight
  The author presents a Python decorator to generate deterministic Python 
  unit tests from existing higher level tests via metaprogramming.  
  %
  This Python decorator hooks function calls in order to record the 
  metadata (input, output, relevant global variables, and code coverage) 
  of each hooked function. 
  %
  The recorded metadata is then used to automatically generate unit 
  tests for each such function.
  %
  % Contribution
  The author's initial testing confirmed that it can 
  be a force multiplier for the developer, 
  as one passing integration or similar test of the overall 
  system can produce many unit tests.  
  %
  As the initial test is designed by the developer, it provides a natural 
  approach to provide expert human insight that is leveraged to create 
  higher quality unit tests.
  %
  Further, many test cases may be generated for each test.  
  Python programmers can save significant time and effort using the 
  generated test cases as boilerplate if more test cases are required to 
  increase coverage.  
  %

\end{abstract}

\keywords{Python, Automated Test Generation, Metaprogramming}

\maketitle

\input{sections/introduction}
\input{sections/assumptions}
\input{sections/approach}
\input{sections/evaluation}
\input{sections/conclusions}

\begin{acks}
  A special thanks to my good friend Brad for his insight and expertise with 
  Python testing and the pytest library.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{related}

\end{document}

% vim: spelllang=en_US
